### 2017-03-13 main.tex
New data. Not yet formatted properly.

% A:
% B: LNY46 0.28s @ 140ms
% C: LNY42 0.38s
% D: LNY4RB 0.25s

Data consisted of extracted, aligned songs, and additional song-length samples of non-song (cage noise, calls, other birds' song). These were divided into training and test sets. For Bird A, we used 1000 songs and 1000 non-song samples for training, and the remaining 1818 songs and 3636 nonsongs for testing. For birds B, C, and D, we used 1000 songs and 1000 non-songs for training, and another 1000 of each for testing.

%\begin{table}
% \begin{tabular}{c|cccc}
%    Bird & Training songs & Test songs & Training non-song & Test non-song \\ %\hline
 %   A & 1000 & 1818 & 1000 & 3636 \\
  %  B & 1000 & 1000 & 1000 & 1000 \\
 %   C & 1000 & 1000 & 1000 & 1000 \\
%    D & 1000 & 1000 &  1000 & 1000
%  \end{tabular}
%  \caption{Sizes of our training and test sets.}
%  \label{table:datasizes}
%\end{table}

@@

Accuracies for our six test syllables are shown in
\fig{fig:accuracies} (accuracies for the synthetic $\delta$-function
songs were always 100\%).  For each test syllable we trained 100
different networks, which differ from each other in the random
initialisation of network weights and on which random subset of our
songs was used for training.  Each network's accuracy is shown as a
single point in each chart in \fig{fig:accuracies}, and the means are
shown in Table~\ref{table:accuracies}.  Evidently some syllables are
easier to identify reliably than others (for example, $t^*_3$ and
$t^*_6$ are occasionally confused due to their similar appearance, as
could be guessed from \fig{fig:song}); thus, if the experimental
design permits, it can be worthwhile to choose an easily identifiable
syllable.  Furthermore, as can be seen from \fig{fig:accuracies}, for
difficult syllables the training process occasionally yields a network
that performs unusually poorly.  It is easy to spot these networks by
their performance either as measured as part of the training process
or on the test audio file, perhaps taking the best of a few training
runs.

@@

\begin{table}
  \begin{tabular}{rc|rr}
    Bird & Target time & \% True positives & \% False positives \\ \hline
    A&$ t^*_1$ & 99.72 &  0.0025 \\
    &$ t^*_2$ & 99.81 &  0.00053 \\
    &$ t^*_3$ & 99.78 &  0.00062 \\
    &$ t^*_4$ & 99.69 &  0.00082 \\
    &$ t^*_5$ & 99.75 &  0.00028 \\
    &$ t^*_6$ & 99.54 &  0.0012 \\
    B&$ t^*$ & 99.37 & 0.0039 \\
    C&$ t^*$ & 99.13 & 0.0011 \\
    D&$ t^*$ & 99.34 &0.0026 \\
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

\noindent Our implementation of the syllable
detector is available under an open-source license {\em (Tentatively GPL, but we are still evaluating which open source license is the most suitable for this software):}
\begin{description}
\item[Training the neural network:]\hfill
  \begin{trivlist}
  \item {\tt https://github.com/gardner-lab/syllable-detector-learn}
  \end{trivlist}

>>>>

% A:
% B: LNY46 0.28s @ 140ms
% C: LNY42 0.38s
% D: LNY4RB 0.25s
% E: LR28 0.14s

\begin{table}
 \begin{tabular}{c|cccccc}
    Bird & Training songs & Test songs & Training non-song & Test non-song & Target time  & Time window length\\ %\hline
   A & 1000 & 1000 & 1000 & 3636 & 150:50:400 & 50 \\
   B & 1000 & 1000 & 1000 & 1000 & 195 & 50 \\
    C & 1000 & 1000 & 1000 & 1000 & 380 & 50 \\
    D & 1000 & 1000 &  1000 & 1000 & 250 & 50 \\
    E & 1000 & 1000 & 1000 & 1000 & 140 & 80
  \end{tabular}
  \caption{Sizes of our training and test sets, times of interest, and detection time window length (milliseconds).}
  \label{table:datasizes}
\end{table}

Data consisted of extracted, aligned songs, and additional song-length
samples of non-song (cage noise, calls, other birds' song). These were
divided into training and test sets. For all birds, we used 1000 songs
and 1000 non-song samples for training. For Bird A we used the
remaining 1818 songs and 3636 nonsongs for testing. For each of the
other birds, we tested on another 1000 songs and 1000
nonsongs. Table~\ref{table:datasizes} lists the dataset sizes, along
with the target detection points and the length of the time history
window used for detection, which was the only parameter that we
adjusted.

@@

Accuracies for our six test syllables for bird A are shown in
\fig{fig:accuracies} (accuracies for the synthetic $\delta$-function
songs were always 100\%).  For each test syllable we trained 100
different networks, which differ from each other in the random
initialisation of network weights and on which random subset of our
songs was used for training.  Each network's accuracy is shown as a
single point in each chart in \fig{fig:accuracies}, and the means are
shown in Table~\ref{table:accuracies}.  Evidently some syllables are
easier to identify reliably than others (for example, $t^*_3$ and
$t^*_6$ are occasionally confused due to their similar appearance, as
could be guessed from \fig{fig:song}); thus, if the experimental
design permits, it can be worthwhile to choose an easily identifiable
syllable.  Furthermore, as can be seen from \fig{fig:accuracies}, for
difficult syllables the training process occasionally yields a network
that performs unusually poorly.  It is easy to spot these networks by
their performance either as measured as part of the training process
or on the test audio file, perhaps taking the best of a few training
runs.

@@

\begin{table}
  \begin{tabular}{rc|rr}
    Bird & Target time & \% True positives & \% False positives \\ \hline
    A&$ t^*_1$ & 99.72 &  0.0025 \\ % lny64
    &$ t^*_2$ & 99.81 &  0.00053 \\
    &$ t^*_3$ & 99.78 &  0.00062 \\
    &$ t^*_4$ & 99.69 &  0.00082 \\
    &$ t^*_5$ & 99.75 &  0.00028 \\
    &$ t^*_6$ & 99.54 &  0.0012 \\
    B&$ t^*$ & 99.370992640000068   0.003887539045000 \\ % lny46
    C&$ t^*$ & 99.218862389999998   0.001205787775200 \\ % lny42
    D&$ t^*$ & 99.342842499999975   0.00260723410200  \\ % lny4rb
    E& $t^*$ & 99.726635259999981   0.003169430259900 \\ % lr28
    E& $t^*$ & 99.464679732673261   0.004515502156436 \\ % lr12
    E& $t^*$ & 99.862406879999966   0.001215710723800 \\ % lr13
    E& $t^*$ & 99.646613329999980   0.003110002775000 % lr77
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

\noindent Our implementation of the syllable
detector is available under the GNU General Public License 3.
\begin{description}
\item[Training the neural network:]\hfill
  \begin{trivlist}
  \item {\tt https://github.com/gardner-lab/syllable-detector-learn}
  \end{trivlist}
